TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-11-05 manuscript/manuscript.Rmd
Reference style for BMC Bioinformatics

---
bibliography: [references/networks.bib,references/brain.bib,references/enrichment.bib,references/3D_refs.bib]
csl: styles.ref/genomebiology.csl
output:
  word_document:
    reference_docx: styles.doc/BMC_Bioinformatics.docx
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

>>>>

---
bibliography: [references/networks.bib,references/brain.bib,references/enrichment.bib,references/3D_refs.bib]
csl: styles.ref/bmc-bioinformatics.csl
output:
  word_document:
    reference_docx: styles.doc/BMC_Bioinformatics.docx
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---
